What do they see? Testing perceptual accuracy  in surveys of the of the general US population using stacked barcharts

### 2023-10-23 SDSS-2023/testing-charts-accuracy.qmd
figure 7 - horizontal

coefs_certainty <- coefs_certainty %>% 
  mutate(
    estimate = scale_x(estimate, from=c(1,5), to=c(0,1)),
    std.error = std.error/4
  )

@@

round_123_certainty_long %>%
  ggplot(aes(x = chart)) +
  facet_grid(.~Question+Correct) +
  geom_bar(aes(fill=Response, weight=weight), 
           position=position_fill(reverse=TRUE), 
           colour="grey40", linewidth=0.25) +
  theme(
    axis.text.x = element_text(angle=30, hjust=1)
  ) + 
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), 
                     labels = seq(0,1, by=0.25)*100, limits = c(-0.1, 1),
                     sec.axis = sec_axis( trans=~(.*4)+1, name="Certainty scores")) +
  xlab("") + 
  scale_fill_brewer("How certain\nare you?", palette = "PRGn", guide = guide_legend(reverse = TRUE)) + 
  geom_point(
    aes(y = estimate),
    size = 3,
    data = coefs_certainty
  ) + 
  geom_errorbar(
    aes(ymin = (estimate-qnorm(0.975)*std.error),
        ymax = (estimate+qnorm(0.975)*std.error)),
    width=0.3,
    data = coefs_certainty
  ) + 
  geom_text(aes(label=letters), y = -0.05, data = coefs_certainty) 
```

>>>>

coefs_certainty <- coefs_certainty %>% 
  mutate(
    estimate = scale_x(estimate, from=c(1,5), to=c(0,1)),
    std.error = std.error/4,
    chart = factor(chart, levels=c("Horizontal wide", "Horizontal", "Vertical"))
  )

@@

round_123_certainty_long <- round_123_certainty_long %>% 
  mutate(
    chart = fct_recode(chart, "Horizontal\nwide" = "Horizontal wide")
  )
coefs_certainty <- coefs_certainty %>% 
  mutate(
    chart = fct_recode(chart, "Horizontal\nwide" = "Horizontal wide")
  )

gg <- round_123_certainty_long %>%
  ggplot(aes(x = chart)) +
  facet_grid(.~Question+Correct) +
  geom_bar(aes(fill=Response, weight=weight), 
           position=position_fill(reverse=TRUE), 
           colour="grey40", linewidth=0.25) +
  theme(axis.text.x = element_text(angle=0, vjust = 0.5)) + 
  #theme(
  #  axis.text.x = element_text(angle=30, hjust=1)
  #) + 
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), 
                     labels = seq(0,1, by=0.25)*100, limits = c(-0.1, 1),
                     sec.axis = sec_axis( trans=~(.*4)+1, name="Certainty scores")) +
  xlab("") + 
  scale_fill_brewer("How certain\nare you?", palette = "PRGn", guide = guide_legend(reverse = TRUE)) + 
  geom_point(
    aes(y = estimate),
    size = 3,
    data = coefs_certainty
  ) + 
  geom_errorbar(
    aes(ymin = (estimate-qnorm(0.975)*std.error),
        ymax = (estimate+qnorm(0.975)*std.error)),
    width=0.3,
    data = coefs_certainty
  ) + 
  geom_text(aes(label=letters), y = -0.05, data = coefs_certainty) #+
#  scale_x_discrete(breaks=c("Horizontal", "Horizontal\nwide", "Vertical"))

#ggb <- ggplot2::ggplot_build(gg)

gg
```
